Experiences with long-term monitoring of a large-scale distributed heterogenous cyberinfrastructure

### 2013-01-03 papers/inca-analysis/Inca-anaylsis.tex
Added the correct Latex template.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@15048 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\documentclass{sig-alternate}
\usepackage{subfigure,url}

@@

\title{}

\numberofauthors{1}

\author{
\alignauthor
Shava Smallen, Sameer Tilak, etc. \\
\affaddr{University of California, San Diego} \\ 
\affaddr{9500 Gilman Drive, La Jolla, CA 92093-0505, USA}\\ 
\email{\{ssmallen,sameer\}@sdsc.edu}\\
}

@@

\section{Introduction}

\section{Future Grid Overview}

@@

\section{Inca Architecture}

\section{Use cases}

\section{Test suite classes}

\section{Experimental results}

\subsection{Monitoring tools comparison:} Ganglia vs Inca

\subsection{reliability}

\subsection{resource-level}: How do different resources (storage, compute, network) compare in terms of reliability. Where is the bottleneck?
\subsection{sw-stack-level}: How do different layers of the s/w stack compare? Where do failures occur the most? Middleware, Apps, OS, etc....
\subsection{site-level}: How do different sites compare in terms of reliability.
\subsection{software-level:} Should we upgrade? History shows newer releases make the system more stable or less stable.
\subsection{cloud-stats}
\subsection{hpc-stats:} benchmarks, version numbers.
\subsection{Failures distribution:} Are failures independent or related?
\subsection{upgrade stats:} Patches done every month. 
\subsection{predictability} Is this system system predictable in terms of resource availability or failures.
\subsection{Test success rate}

\section{Future Work}

\section{Conclusion}

>>>>

\documentclass{IEEEtran}
\usepackage{subfigure,url}

@@

\title{Experiences with long-term monitoring of a large-scale distributed heterogenous cyberinfrastructure}

\author{\IEEEauthorblockN{Shava Smallen and Sameer Tilak}
\IEEEauthorblockA{ University of California, San Diego \\
La Jolla, CA, USA, Email: {\{ssmallen,stilak\}}@ucsd.edu}
}

@@

\section{Introduction} (0.5 page)

\section{Future Grid Overview} (1 page)
Add description of load -- vm count, hrs. etc.

@@

\section{Inca Architecture} (0.5 page)

Cyberinfrastructure (CI) aggregates multiple complex and interdependent systems that span several administrative domains. This complexity poses challenges for both administrators who build and maintain CI resources and scientists who use them.  These challenges and the cutting-edge nature of the infrastructure make it susceptible to failures, which frustrate and even dissuade users.  In order to provide scientists with persistent and reliable CI, the user-level functionality and performance of the system must be monitored.  Developed in 2003, Inca [1] is a tool that provides user-level monitoring for CI systems. It has proven to be a valuable tool for the TeraGrid [2] and eleven other production CI projects [3], and is currently monitoring over a hundred machines.   Inca differs from other monitoring tools with its user-level monitoring approach, flexibility to collect multiple types of monitoring data, and full archiving support.  Inca also uses a unique centralized monitoring configuration approach, which is essential for providing consistent monitoring results and a unified and coherent infrastructure for users.

Inca automates the installation, execution, and maintenance of a large variety and number of reporters (monitoring scripts) consistently across Grid resources.   Monitoring results are collected, archived, and displayed through web status pages.   The core of the Inca architecture is formed by four server components: the agent, depot, data consumer, and reporter repository (see Figure 1).  The agent controls the deployment and maintenance of the Inca installation, while the depot provides data storage.  A reporter repository contains a set of tests and benchmarks, and the data consumer displays the collected results as web status pages.  An additional Inca component called the reporter manager runs on each monitored resource to collect status and performance data.  The final component of Inca is a GUI tool (incat) used by Inca administrators to configure and maintain their Inca deployments.

Recently, we have been exploring how to leverage Inca in virtual Cloud environments as part of the work we are doing in FutureGrid [4].  FutureGrid is an experimental testbed that will be used to develop and test novel approaches to parallel, grid, and cloud computing.  It supports user “experiments” that can be run either on the bare hardware or on virtual machines using Cloud technologies Nimbus or Eucalyptus.   In particular, we are interested in using Inca to validate a user’s virtual environment started up by these tools both in terms of functionality and performance.  For example, a user may want to know how the performance of their virtual cluster compares to a month earlier when they last instantiated it. We are also interested in using Inca to validate individual virtual machine images as well.

\section{Use cases} (0.5 pages)

\section{Test suite classes} (0.5 pages)

\section{Analysis results} (4 pages)
Description of the methodology -- how data was filtered and interpreted.

\subsection{SSH data}
\subsubsection{Failure Classifiation:} What types of failures do we see?
\subsubsection{Failures distribution:} Are failures independent or related?
\subsubsection{predictability} Is this system system predictable in terms of resource availability or failures.
\subsection{site-level}: How do different sites compare in terms of reliability.

ssh key -- test improvements.

\subsection{cloud-stats}
\subsection{hpc-stats:} benchmarks, version numbers.

\subsection{sw-stack-level}: How do different layers of the s/w stack compare? Where do failures occur the most? Middleware, Apps, OS, etc....
\subsection{software-level:} Should we upgrade? History shows newer releases make the system more stable or less stable.
\subsection{upgrade stats:} Patches done every month.

\section{Related Work} (0.5 page)

\section{Future Work} (0.25 page)

\section{Conclusion} (0.25 page)
